Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2020-04-30 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
IEEE paper update

Fig.\ref{fig:blockdiagram} illustrates a stand-alone PV system block diagram. The PV generator (a panel or an array) is a semiconductor device that can convert solar energy into DC electricity. For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required. The AC load dictates the AC electrical load behaviour from the house.
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

@@

In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions; except for the automated synthesis where we also define the bound $k$ to restrict the design-space search. Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost. On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables. Furthermore, as described in this section, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparative of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

To perform the automated formal synthesis, we use a state-of-the-art model checker. ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing. Datasheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase. 
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{https://drive.google.com/file/d/1uOWXdQqkKMNxHLj66S-QxTriVioLxpcv/view?usp=sharing}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions and Premises}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}}.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c}
\hline
\hline
Tools & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result\\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & UNSAT (0.48 min) & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: TO= time out; E= energy; NTP= total number of panels, NBtotal= total number of batteries, NPS= number of panels in series; NPP= number of panels in parallel, NBS= number of batteries in series; NBP= number of batteries in parallel; LCC= Life Cycle Cost.
\end{scriptsize}
\end{table}

@@

The state-of-art verification tool ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer} was used as our reference verification engine. The optimization tool HOMER Pro version $3.13.1$ was used for comparative purpose. The optimal sizing produced by ESBMC and HOMER Pro are validated with tool PVsyst v$6.86$~\cite{PVsyst}. PVsyst is a MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment. PVsyst does not perform optimization nor does it have commercial inverter equipment.

@@

\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c}
\hline
\hline
CS & \makecell{PVsyst\\(pre-sizing)}&\makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
\hline
\hline
CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.16$\times$\\Batteries oversized: 1.39$\times$}\\
\hline
CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)}&\makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.6$\times$\\Batteries oversized: 1.74$\times$}\\
\hline
CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} &\makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)}&\makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized: 2.24$\times$\\Batteries oversized: 1.41$\times$}\\
\hline
CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 1.93$\times$\\Batteries oversized:  1.56$\times$}\\
\hline
CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.42$\times$\\Batteries oversized: 1.38$\times$}\\
\hline
CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)}&\makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.9$\times$\\Batteries oversized: 1.99$\times$}\\
\hline
\hline
\end{tabular}
\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater).
\end{scriptsize}
\end{table}

>>>>

Fig.\ref{fig:blockdiagram} illustrates a stand-alone PV system block diagram. The PV generator (a panel or an array) is a semiconductor device that can convert solar energy into DC electricity. For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC, and therefore when the PV system contains an AC load, a DC/AC conversion (inverter) is required. The AC load dictates the AC electrical load behaviour from the house.
%
\begin{figure}[h]
\hspace*{-1cm}\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

@@

In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions; except for the automated synthesis where we also define the bound $k$ to restrict the design-space search. Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost. On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables. Furthermore, as described in this section, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
%
\begin{figure}[h]
\hspace*{-1cm}\includegraphics[width=0.55\textwidth]{optimalsizingprocess4}
\centering
\caption{Comparative of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

@@

To perform the automated formal synthesis, we use a state-of-the-art model checker. ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{\url{http://smtlib.cs.uiowa.edu/}} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing. Data-sheet from each item was necessary to collect technical information\footnote{\url{http://tiny.cc/4ny4nz}}. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. %All this data is available online\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The challenge for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase. 
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The Algorithm~\ref{alg:verification-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verify ($C \wedge \neg P$), as shown online\footnote{\url{http://tiny.cc/ity4nz}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions and Premises}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. %All this data is available online\footnote{\url{https://drive.google.com/file/d/1XOQMC0zdybvTLyBLo-TlChLdwDFUlUCT/view?usp=sharing}}.

@@

\begin{table}
\caption{Case studies and results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c}
\hline
\hline
Tools & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result\\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (620 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 700W/48V\\LCC: US\$ 10,214.04} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell{SAT (63 min) \\NTP:14$\times$150W (7P-2S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 35A/145V\\Inverter 1,200W/48V\\LCC: US\$ 9,274.07} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & \makecell{SAT (147 min) \\NTP:6$\times$330W (2P-3S)\\NBT:16$\times$105Ah (2S-8P)\\Controller 35A/145V\\Inverter 280W/48V\\LCC: US\$ 9,678.63} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (36.70 min) \\NTP:4$\times$330W (2S-2P)\\NBT:14$\times$80Ah (2S-7P)\\Controller 35A/145V\\Inverter 280W/24V \\LCC: US\$ 8,900.70} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (380.93 min) \\NTP:6$\times$320W (2P-3S)\\NBT:18$\times$105Ah (2S-9P)\\Controller 35A/145V\\Inverter 400W/24V \\LCC: US\$ 10,136.61} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & UNSAT (0.48 min) & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: TO= time out; E= energy; NTP= total number of panels, NBtotal= total number of batteries, NPS= number of panels in series; NPP= number of panels in parallel, NBS= number of batteries in series; NBP= number of batteries in parallel; LCC= Life Cycle Cost.
\end{scriptsize}
\end{table}

@@

The state-of-art verification tool ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-incremental-bmc -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer} was used as our reference verification engine. The optimization tool HOMER Pro version $3.13.1$ was used for comparative purpose. The optimal sizing produced by ESBMC and HOMER Pro were validated with PVsyst v$6.86$~\cite{PVsyst}. PVsyst is a MS-Windows software used for the study, sizing, simulation, and data analysis of solar PV systems, with a comprehensive list of commercial equipment. PVsyst does not perform optimization. % nor does it have commercial inverter equipment.

@@

\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c}
\hline
\hline
\makecell{Case\\Study} & \makecell{PVsyst\\(pre-sizing)}&\makecell{Formal synthesis\\optimal sizing\\validation}& \makecell{HOMER Pro\\optimal sizing\\validation}\\
\hline
\hline
\# 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.16$\times$\\Batteries oversized: 1.39$\times$}\\
\hline
\# 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)}&\makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.6$\times$\\Batteries oversized: 1.74$\times$}\\
\hline
\# 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} &\makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
\# 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)}&\makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized: 2.24$\times$\\Batteries oversized: 1.41$\times$}\\
\hline
\# 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 1.93$\times$\\Batteries oversized:  1.56$\times$}\\
\hline
\# 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)}&\makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized: 2.42$\times$\\Batteries oversized: 1.38$\times$}\\
\hline
\# 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)}&\makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized: 2.9$\times$\\Batteries oversized: 1.99$\times$}\\
\hline
\hline
\end{tabular}
\\Legend: NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater).
\end{scriptsize}
\end{table}
